An Example Article using \aastex v6.2\footnote{Released on January, 8th, 2018}

### 2018-02-10 paper/ms.tex
update paper

Briefly, the PSF photometry problem that lightkurve solves can be formulated as
follows. Given an image $\bm{y}$, with $n$ pixels and $m$ stars, and a PSF model
$\lambda(\bm{\theta}) = \sum_{j=1}^{m} \lambda({\theta}_j)$,
find the best parameter vector
$\bm{\theta}^{\star} = (\theta_1^{\star}, \theta_2^{\star}, ..., \theta_m^{\star})$
that minimizes some cost (or loss) function $R(\lambda(\bm{\theta}), \bm{y})$
of assigning $\bm{\theta} = \bm{\theta}^{\star}$.

From a probabilistic point of view, one is often interested in minimizing the
expected cost with respect to some probability distribution assigned to the data
$\bm{y}$ and to the parameter vector $\bm{\theta}$, from which the cost function
$R$ naturally arises. The default assumption on the data is that it follows
a Poisson probability distribution, whereas the probability distribution on the
parameter vector has to be assigned by the user using the $\texttt{prior}$
argument. Using a uniform prior for $\bm{\theta}$, the MAP estimator can be written
as
\begin{align}
    \bm{\theta}^{\star}(\bm{y}) = \argmin_{\bm{\theta} \in \Lambda} \sum_{i=1}^{n}
    \left(\sum_{j=1}^{m}\lambda_i(\bm{\theta}_j) - y_i\log\sum_{j=1}^{m}\lambda_i(\bm{\theta}_j)\right),
\end{align}
in which $\Lambda$ is the support of $\bm{\theta}$.

@@

Spacecraft-induced correlated noise remains one of the greatest hurdles to
analyzing K2 lightcurves. Many algorithms have been developed to mitigate
motion-dependent artifacts~\cite{vanderburg14}. In \lightkurve~we implement
an algorithm based off of~\cite{vanderburg14}

>>>>

Briefly, the PSF photometry problem that \lightkurve~solves can be formulated as
follows. Given an image $\bm{y}$, with $n$ pixels and $m$ stars, and a PSF model
$\lambda(\bm{\theta}) = \sum_{j=1}^{m} \lambda({\theta}_j)$,
find the best parameter vector (which encodes fluxes and center positions for $m$
stars) $\bm{\theta}^{\star} = (\theta_1^{\star}, \theta_2^{\star}, ..., \theta_m^{\star})$
that minimizes some cost (or loss) function $R(\lambda(\bm{\theta}), \bm{y})$
of assigning $\bm{\theta} = \bm{\theta}^{\star}$.

From a probabilistic point of view, one is often interested in minimizing the
expected cost with respect to some probability distribution assigned to the data
$\bm{y}$ and to the parameter vector $\bm{\theta}$, from which the cost function
$R$ naturally arises. The default assumption, made in \lightkurve,~on the data is
that it follows a Poisson probability distribution, whereas the probability
distribution on the parameter vector has to be assigned by the user using the $\texttt{prior}$
argument. Using a uniform prior for $\bm{\theta}$, the MAP estimator can be written
as
\begin{align}
    \bm{\theta}^{\star}(\bm{y}) = \argmin_{\bm{\theta} \in \Lambda} \sum_{i=1}^{n}
    \left(\sum_{j=1}^{m}\lambda_i(\bm{\theta}_j) - y_i\log\sum_{j=1}^{m}\lambda_i(\bm{\theta}_j)\right),
\end{align}
in which $\Lambda$ is the support of $\bm{\theta}$.

@@

Spacecraft-induced correlated noise remains one of the greatest hurdles to
analyzing K2 lightcurves. Many algorithms have been developed to mitigate
motion-dependent artifacts~\cite{vanderburg14}[CITE K2SC and EVEREST].
In \lightkurve, we implement an algorithm based off of the self-flat-field
(SFF) presented in~\cite{vanderburg14}.

Basically, SFF works by decorrelating the simple aperture flux
against the information on the spacecraft motion, obtained by computing the
arclength using the centroids of the target.

\begin{verbatim}
from lightkurve import KeplerTargetPixelFile
tpf = KeplerTargetPixelFile("ktwo248667471-c14_lpd-targ.fits.gz")
lc = tpf.to_lightcurve()
centroids = tpf.get_centroids()
lcc = lc.correct(centroids[0], centroids[1])
\end{verbatim}
